```{r setup, include = FALSE}
library(lipsum)
```

# Separator slide heading 1 extra text a b c d e f g h i j k l m n o p q r s t u v w x y z 0 1 2 3 4 5 6 7 8 9 a b c d e f g h i j k l m n o p q r s t u v w x y z 0 1 2 3 4 5 6 7 8 9

## Slide title extra text a b c d e f g h i j k l m n o p q r s t u v w x y z 0 1 2 3 4 5 6 7 8 9 a b c d e f g h i j k l m n o p q r s t u v w x y z 0 1 2 3 4 5 6 7 8 9 

- The text box will automatically shrink when the slide title requires more lines
- The text is vertically centred within the text box
- In case the title of heading 1 is too long, the first part of the title will disappear

## Slide with too much text

- The last part of the text will disappear if it doesn't fit the slide
- The font size will not shrink to fit the text (like PowerPoint does)

`r paragraph(1:2)`

# Fonts 

## Normal font

`r paragraph()`

## Italic font

_`r paragraph()`_

## Bold font

**`r paragraph()`**

## Bold and italic font

**_`r paragraph()`_**

## Fixed width font

```{r fixed-width, echo = FALSE, results = "asis"}
cat("`", paragraph(), "`", sep = "")
```

## Available number of characters per line

About 69 characters with normal font

12345678911234567892123456789312345678941234567895123456789612345678971234567898

_12345678911234567892123456789312345678941234567895123456789612345678971234567898_

About 62 characters with bold font

**12345678911234567892123456789312345678941234567895123456789612345678971234567898**

**_12345678911234567892123456789312345678941234567895123456789612345678971234567898_**

62 characters with fixed width font

`12345678911234567892123456789312345678941234567895123456789612345678971234567898`

## Minuscule L versus capital i

normal:
  ~ lI <!-- spell-check: ignore -->

bold:
  ~ **lI** <!-- spell-check: ignore -->
  
italics:
  ~ _lI_ <!-- spell-check: ignore -->
  
bold italics:
  ~ **_lI_** <!-- spell-check: ignore -->

fixed width font:
  ~ `lI` <!-- spell-check: ignore -->

## Special characters

€$£ @&#§µ^ ()[]{}|²³<>/\*+- ,;:.?!~ äàáâã ëèéê ïìíî öòóô üùúû ÿ ç ñ ÄÀÁÂ ËÈÉÊ ÏÌÍÎ ÖÒÓÔ ÜÙÚÛ Ñ 0123456789 <!-- spell-check: ignore -->

_€$£ @&#§µ^ ()[]{}|²³<>/\*+- ,;:.?!~ äàáâã ëèéê ïìíî öòóô üùúû ÿ ç ñ ÄÀÁÂ ËÈÉÊ ÏÌÍÎ ÖÒÓÔ ÜÙÚÛ Ñ 0123456789_ <!-- spell-check: ignore -->

**€$£ @&#§µ^ ()[]{}|²³<>/\*+- ,;:.?!~ äàáâã ëèéê ïìíî öòóô üùúû ÿ ç ñ ÄÀÁÂ ËÈÉÊ ÏÌÍÎ ÖÒÓÔ ÜÙÚÛ Ñ 0123456789** <!-- spell-check: ignore -->

**_€$£ @&#§µ^ ()[]{}|²³<>/\*+- ,;:.?!~ äàáâã ëèéê ïìíî öòóô üùúû ÿ ç ñ ÄÀÁÂ ËÈÉÊ ÏÌÍÎ ÖÒÓÔ ÜÙÚÛ Ñ 0123456789_** <!-- spell-check: ignore -->

`€$£ @&#§µ^ ()[]{}|²³<>/\*+- ,;:.?!~ äàáâã ëèéê ïìíî öòóô üùúû ÿ ç ñ ÄÀÁÂ ËÈÉÊ ÏÌÍÎ ÖÒÓÔ ÜÙÚÛ Ñ 0123456789` <!-- spell-check: ignore -->

## Quotation marks

normal:
  ~ "double", 'single'

bold:
  ~ **"double", 'single'**

italics:
  ~ _"double", 'single'_

bold italics:
  ~ **_"double", 'single'_**

fixed width font:
  ~ `"double", 'single',`

# Lists

## Unordered list

- First level
- The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.
- Item 3
    - Second level
        - Third level
        - The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.
    - The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. 

## Ordered list

1. First level
1. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.
1. Item 3
    1. Second level
        1. Third level
        1. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.
    1. The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.

## Incremental list

::: {.incremental}
- First level
- The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.
- Item 3
    - Second level
        - Third level
        - The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.
    - The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog. 
:::

## List with pauze

- First level

. . .

- The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.

. . .

  - Item 3
- The quick brown fox jumps over the lazy dog. The quick brown fox jumps over the lazy dog.
